### 2021-03-20 papers.tex
Updated table of contents to include 2021 papers (the early ones)

\newpage
\renewcommand{\thepage}{\arabic{page}}
\setcounter{page}{1}
\addproceedings{Table of COVID-tense}

@@

\addtrack
	{}{Reading Skills}
\addpaper
	{Anonymous paper}
	{Anonymous Author}
	{Keywords: anonymous, triple blind, review}
	{SIGBOVIK_2020_paper_1}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_7}{0cm}
\addpaper
	{State-of-the-Art Reviewing: A radical proposal to improve scientific publication}
	{Samuel Albanie, Jaime Thewmore, Robert McCraith, Jo\~ao F.\@ Henriques}
	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}
	{SIGBOVIK_2020_paper_38}
	{0cm}
	{}

\addtrack
	{}{SIGBOVIK}
\addpaper
	{A thorough investigation of the degree to which the COVID-19 pandemic has enabled subpar-quality papers to make it into the proceedings of SIGBOVIK, by reducing the supply of authors willing to invest the necessary effort to produce high-quality papers}
	{Shalin Shah}
	{Keywords: COVID-19, SIGBOVIK, lazy, quality, sadness, big Oof}
	{SIGBOVIK_2020_paper_36}
	{0cm}
	{}
\addpaper
	{Is this the longest Chess game?}
	{Dr.\@ Tom Murphy VII Ph.D.}
	{Keywords: chess, chesses, chessing, G.\@ K.\@ Chesterton}
	{SIGBOVIK_2020_paper_28}
	{0cm}
	{}
\addpaper
	{Optimizing the SIGBOVIK 2018 speedrun}
	{leo60228}
	{Keywords: speedrun, SIGBOVIK, pathfinding, DFS, Rust}
	{SIGBOVIK_2020_paper_20}
	{0cm}
	{}
\addpaper
	{Retraction of a boring follow-up paper to ``Which ITG stepcharts are turniest?'' titled, ``Which ITG stepcharts are crossoveriest and/or footswitchiest?''}
	{Ben Blum}
	{Keywords: groove, in, retraction, the}
	{SIGBOVIK_2020_paper_18}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_9}{0cm}

\addtrack
	{}{Programming Languages}
\addpaper
	{Ntinuation copassing style}
	{Cameron Wong, Dez Reed}
	{Keywords: continuation, ntinuation, control flow, programming languages}
	{SIGBOVIK_2020_paper_33}
	{0cm}
	{}
\addpaper
	{Formulating the syntactically simplest programming language}
	{Brendon Boldt}
	{Keywords: proramming languages, compilers, formal grammars}
	{SIGBOVIK_2020_paper_12}
	{0cm}
	{}
\addpaper
	{Type-directed decompilation of shell scripts}
	{Spencer Baugh, Dougal Pugson}
	{Keywords: partial evaluation, type systems, shell scripting}
	{SIGBOVIK_2020_paper_25}
	{0cm}
	{}
\addpaper
	{Verified proof of P=NP in the Silence theorem prover language}
	{Matias Scharager}
	{Keywords: soundness, P=NP, theorem prover, Silence, programming language theory, type theory}
	{SIGBOVIK_2020_paper_29}
	{0cm}
	{}

\addtrack
	{}{Systems}
\addpaper
	{SIGBOVIK '75 technical note: Conditional move for shell script acceleration}
	{Dr.\@ James McCann, Dr.\@ Tom Murphy VII}
	{Keywords: cond-, itional, move}
	{SIGBOVIK_2020_paper_32}
	{0cm}
	{}
\addpaper
	{NaN-gate synthesis and hardware deceleration}
	{Cassie Jones}
	{Keywords: hardware deceleration, hardware synthesis, electronic design automation, IEEE-754, NaN-gates, cat meme}
	{SIGBOVIK_2020_paper_19}
	{0cm}
	{}
\addpaper
	{hbc: A celebration of undefined behavior}
	{Andrew Benson}
	{Keywords: compilers, undefined behavior, Bash misuse, computer music, Principles of Imperative Computation}
	{SIGBOVIK_2020_paper_34}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_3}{0cm}

\addtrack
	{}{Theory}
\addpaper
	{A polynomial-time SAT algorithm}
	{Anonymous Author(s)}
	{Keywords: theoretical computer science, complexity theory, p versus np}
	{SIGBOVIK_2020_paper_2}
	{0cm}
	{}
\addpaper
	{Empire Machines and beyond}
	{Dar\'io de la Fuente Garc\'ia, F\'elix \'Axel Gimeno Gil, Juan Carlos Morales Vega}
	{Keywords: finite-state machines, models of computation, Empire Machines, doing research like this is awesome, Civilization XXIV (when it comes out)}
	{SIGBOVIK_2020_paper_16}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_8}{0cm}
\addpaper
	{Artificial General Relativity}
	{Pablo Samuel Castro}
	{Keywords: physics, artificial, general relativity, quantum physics, universe-changing, new science, field equations, black holes}
	{SIGBOVIK_2020_paper_14}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_5}{0cm}
\addpaper
	{Making explicit a constant appearing in an impossible equation of Carl and Moroz}
	{Matthew Weidner}
	{Keywords: computational mathematics, Hilbert's tenth problem, Diophantine sets}
	{SIGBOVIK_2020_paper_8}
	{0cm}
	{}

\addtrack
	{}{Security}
\addpaper
	{Determining the laziest way to force other people to generate random numbers for us using IoT vulnerabilities}
	{mathmasterzach, StarChar}
	{Keywords: babies, information theory, randomness, entropy, April fools, hacking, the law, coffee shops, smart-toasters}
	{SIGBOVIK_2020_paper_4}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_6}{0cm}
\addpaper
	{Putting the ceremony in ``authentication ceremony''}
	{Camille Cobb, Sruti Bhagavatula}
	{Keyword: authentication, ceremony, fun, security, weddings}
	{SIGBOVIK_2020_paper_23}
	{0cm}
	{}

\addtrack
	{}{Artificial Intelligence \& Machine Learning}
\addpaper
	{Image2image neural network for addition and subtraction evaluation of a pair of not very large numbers}
	{Vladimir Ivashkin}
	{Keywords: neural network, computer vision, calculator}
	{SIGBOVIK_2020_paper_6}
	{0cm}
	{}
\addpaper
	{Robot ethics:\@ Dangers of reinforcement learning}
	{Jake Olkin}
	{Keywords: deep reinforcement learning, ethics, simulation, spoof}
	{SIGBOVIK_2020_paper_24}
	{0cm}
	{}
\addpaper
	{Learning to be wrong via gradient ascent: A broken clock is right twice a day, but a clock that runs backwards can be used to tell the time!}
	{Alex Meiburg}
	{Keywords: machine learning, gradient descent, loss landscape, logistic regression, biased estimators, eliminating bias, overtraining}
	{SIGBOVIK_2020_paper_35}
	{0cm}
	{}
\addpaper
	{GradSchoolNet:\@ Robust end-to-end *-shot unsupervised deepAF neural attention model for convexly optimal (artifically intelligent) success in computer vision research}
	{Divam Gupta, Varun Jain}
	{Keywords: none, haha, nono}
	{SIGBOVIK_2020_paper_17}
	{1.8cm}
	{}
\addreview{SIGBOVIK_2020_review_10}{0cm}

\addtrack
	{}{Natural Intelligence \& Human Learning}
\addpaper
	{Sorting with human intelligence}
	{Cole Kurashige}
	{Keywords: sorting, algorithm, crowd sourcing, human intelligence}
	{SIGBOVIK_2020_paper_22}
	{0cm}
	{}
\addpaper
	{Synthesizing programs by asking people for help online}
	{Cassie Jones}
	{Keywords: program synthesis, cloud computing, social computation, the real program synthesizer was the friends we made along the way}
	{SIGBOVIK_2020_paper_15}
	{0cm}
	{}
\addpaper
	{HonkFast, PreHonk, HonkBack, PreHonkBack, HERS, AdHonk and AHC:\@ The missing keys for autonomous driving}
	{Bernhard Egger, Max Siegel}
	{Keywords: awesome paper, best paper award, great reviewer 3, awesome reviewer 2, marvelous reviewer 1}
	{SIGBOVIK_2020_paper_27}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_11}{0cm}

\addtrack
	{}{Education}
\addpaper
	{A disproof of the Theorem of Triviality}
	{Arul Kolla, August Deer, Ethan Kogan}
	{Keywords: theorem of triviality, theorem, meta problems, meta, math i guess}
	{SIGBOVIK_2020_paper_5}
	{0cm}
	{}
\addpaper
	{Visualizing player engagement with virtual spaces using GIS}
	{Frederick Chan}
	{Keywords: geographic information systems, virtual spaces, video games, video game anthropology}
	{SIGBOVIK_2020_paper_3}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_2}{0cm}

\addtrack
	{}{Blockchain Gang}
\addpaper
	{RegisToken}
	{Irene Lin, Arnaud Avondet, Preston Vander Vos}
	{Keywords: blockchain, Ethereum, token, FCE, course registration}
	{SIGBOVIK_2020_paper_10}
	{0cm}
	{}

\addtrack
	{}{\LARGE The SIGBOVIK 2020 Field Guide to Conspiracy Theories}
\addpaper
	{Faking ancient computer science:\@ A special SIGBOVIK tutorial}
	{Roxanne van der Pol, Brian van der Bijl, Diederik M.\@ Roijers}
	{Keywords: ancient computer science, aliens, conspiracy theories, Triangle of Conspiracy Succession, probability, Arcaicam Esperantom, random number generator, pseudo-science}
	{SIGBOVIK_2020_paper_7}
	{0cm}
	{}
\addpaper
	{MORSE OF COURSE:\@ Paper reveals time dimension wasted}
	{Dougal Pugson}
	{Keywords: Morse code, performance, Bash, protocols}
	{SIGBOVIK_2020_paper_26}
	{0cm}
	{}
\addpaper
	{The Pacman effect and the Disc-Sphere Duality}
	{Francisco Ferreira, Fulvio Gesmundo, Lorenzo Gheri, Pietro Gheri, Riccardo Pietracaprina, Fangyi Zhou}
	{Keywords: Pacman, peace, Earth, flat, round, disc, sphere}
	{SIGBOVIK_2020_paper_37}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_4}{0cm}

\addtrack
	{}{Serious Business}
\addpaper
	{The SIGBOVIK 2020 field guide to plants}
	{Jim McCann (editor)}
	{Keywords: field guide, plants, to}
	{SIGBOVIK_2020_paper_31}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_12}{0cm}
\addpaper
	{Deep industrial espionage}
	{Samuel Albanie, James Thewlis, Sebastien Ehrhardt, Jo\~ao F.\@ Henriques}
	{Keywords: late, very late, so extremely late}
	{SIGBOVIK_2019_paper_43}
	{1.8cm}
	{}
\addpaper
	{What is the best game console?: A free-market--based approach}
	{Dr.\@ Tom ``I Only Write Chess Papers Now'' Murphy VII Ph.D.}
	{Keywords: invisible hand, handheld console, minimum of 3 keywords}
	{SIGBOVIK_2020_paper_30}
	{0cm}
	{}

\addtrack
	{}{Funny Business}
\addpaper
	{Can a paper be written entirely in the title? 1. Introduction: The title pretty much says it all. 2. Evaluation: It gets the job done. However, the title is a little long. 3. Conclusion: Yes.}
	{Daniel Gaston}
	{Keywords: innovation, strength, progress}
	{SIGBOVIK_2020_paper_9}
	{0cm}
	{}
\addreview{SIGBOVIK_2020_review_1}{0cm}
\addpaper
	{Erd\"os-Bacon-Sabbath numbers: \textit{Reductio ad absurdum}}
	{Maria Klawe \textit{et al.}\@ (incl.\@ Harry Q.\@ Bovik!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!1)}
	{Keywords: Paul Erd\"os, Kevin Bacon, Black Sabbath}
	{SIGBOVIK_2020_paper_11}
	{0cm}
	{}

>>>>

\newpage
\renewcommand{\thepage}{\arabic{page}}
\setcounter{page}{1}
\addproceedings{Blindsight is also 2021}

@@

\addtrack
	{}{Big Dummy Track}
\addpaper
	{Refutation of the “Failure to remove the template text from your paper may result in your paper not being published” Conjecture}
	{Nicolas Hurtubise}
	{Keywords: anonymous, triple blind, review}
	{SIGBOVIK_2021_paper_1}
	{0cm}
	{}
\addpaper
	{Stop Doing Type Theory}
	{Jason Reed}
	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}
	{SIGBOVIK_2021_paper_2}
	{0cm}
	{}

\addpaper
	{``The SIGBOVIK paper to end all SIGBOVIK papers'' will not be appearing at this conference}
	{Thomas Chick}
	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}
	{SIGBOVIK_2021_paper_3}
	{0cm}
	{}
\addpaper
	{SIGBOVIK 2021 isn't named SIGCOVID}
	{Cameron Wong}
	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}
	{SIGBOVIK_2021_paper_4}
	{0cm}
	{}
\addpaper
	{Back to Square One: Superhuman Performance in Chutes and Ladders Through Deep Neural Networks and Tree Search}
	{Dylan Ashley, Anssi Kanervisto and Brendan Bennett}
	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}
	{SIGBOVIK_2021_paper_5}
	{0cm}
	{}
\addpaper
	{The Urinal Packing Problem in Higher Dimensions}
	{Shane Guan, Skanda Kaashyap and Blair Chen}
	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}
	{SIGBOVIK_2021_paper_6}
	{0cm}
	{}
\addpaper
	{How to get to second base and beyond - a constructive guide for mathematicians}
	{Raluca Jalaboi and Mads Eiler Hansen}
	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}
	{SIGBOVIK_2021_paper_7}
	{0cm}
	{}
\addpaper
	{Universal Insights with Multi-layered Embeddings}
	{Fred Buchanan, Sam Cohen and James Flamino}
	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}
	{SIGBOVIK_2021_paper_8}
	{0cm}
	{}
\addpaper
	{openCHEAT: Computationally Helped Error bar Approximation Tool - Kickstarting Science 4.0}
	{Bernhard Egger, Kevin Smith and Max Siegel}
	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}
	{SIGBOVIK_2021_paper_9}
	{0cm}
	{}
\addpaper
	{AI is a Really, Really, Really Bad Idea}
	{Molly de Blanc}
	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}
	{SIGBOVIK_2021_paper_10}
	{0cm}
	{}
\addpaper
	{Revenge of the pith: Surveying the landscape of plant-powered scientific literature}
	{Vinay Prabhu}
	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}
	{SIGBOVIK_2021_paper_11}
	{0cm}
	{}
\addpaper
	{Demystifying the Mortal Kombat Song}
	{J Devi and Chai-Tea Latte}
	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}
	{SIGBOVIK_2021_paper_12}
	{0cm}
	{}
\addpaper
	{Unicode Magic Tricks}
	{Nicolas Hurtubise}
	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}
	{SIGBOVIK_2021_paper_13}
	{0cm}
	{}
\addpaper
	{Stone Tools as Palaeolithic Central Unit Processors}
	{Efrati Benjamin}
	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}
	{SIGBOVIK_2021_paper_14}
	{0cm}
	{}
\addpaper
	{Winning the Rankings Game: A New, Wonderful, Truly Superior CS Ranking}
	{Mary Shaw}
	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}
	{SIGBOVIK_2021_paper_15}
	{0cm}
	{}
\addpaper
	{Solving reCAPTCHA v2 Using Deep Learning}
	{David Krajewski and Eugene Li}
	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}
	{SIGBOVIK_2021_paper_16}
	{0cm}
	{}
\addpaper
	{Deep Deterministic Policy Gradient Boosted Decision Trees}
	{Clayton Thorrez}
	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}
	{SIGBOVIK_2021_paper_17}
	{0cm}
	{}
\addpaper
	{Video games in Fonts Fontemon}
	{Michael Mulet}
	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}
	{SIGBOVIK_2021_paper_18}
	{0cm}
	{}
\addpaper
	{Build your own 8-bit busy beaver on a breadboard!}
	{Robert Simmons}
	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}
	{SIGBOVIK_2021_paper_19}
	{0cm}
	{}
\addpaper
	{On Sigbovik Paper Maximization}
	{Josh Abrams}
	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}
	{SIGBOVIK_2021_paper_20}
	{0cm}
	{}
\addpaper
	{Oracle Types}
	{Jason Reed and Akiva Leffert}
	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}
	{SIGBOVIK_2021_paper_21}
	{0cm}
	{}
\addpaper
	{Instruction Programs}
	{James McCann}
	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}
	{SIGBOVIK_2021_paper_22}
	{0cm}
	{}
\addpaper
	{Inverted Code Theory: Manipulating Program Entropy}
	{Alan Hsu and Alex Xie}
	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}
	{SIGBOVIK_2021_paper_23}
	{0cm}
	{}
\addpaper
	{Yet Another Lottery Ticket Hypothesis}
	{Aman Madaan and Gary Yao}
	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}
	{SIGBOVIK_2021_paper_24}
	{0cm}
	{}
